Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-10-18 response.tex

\introcomment{~}{%
Review of Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity by Naeem Khoshnevis, Ricardo Taborda, Shima Azizzadeh-Roodpish, and Chris H. Cramer
}

\introcomment{~}{%
In this paper, the researchers present a new seismic hazard analysis of northern Iran. The paper makes use of the latest available data and methods, is thorough in its review of previous work, and is very well presented and written. I have a few suggestions that I think would improve the impact of their results. The annotated version of the manuscript contains additional and more specific suggestions.
}

\comment{1}{%
The authors present uncertainty in their hazard estimate but do not include a more exhaustive logic tree analysis. Effectively, they have two branches: a regional model and uniform model. It appears that they apply the aleatory uncertainty in the ground motion prediction relation to a form of epistemic uncertainty, effectively double counting this uncertainty in the hazard analysis. I would prefer to see a more standard logic tree analysis where multiple GMPEs (or a backbone plus and minus one standard deviation) and uncertainty in a-value, b-value, and Mmax, for example, are considered. Barring this analysis, I would remove figure 10 and references to hazard uncertainty.
}

\response{Thanks for the comment.  Based on explanation of GMPEs section (please see comment no.27) we decided to define a suite of GMPE as well as plus and minus one standard deviation. We consider the epistemic uncertainty in tectonic seismic regions, $M_{max}$, $b-value$, and attenuation relationship through a standard logic tree analysis.}.

@@

\comment{2}{%
While I think that the regional and uniform models are generally correct within 1.5 degrees of the border, I think that outside of this region, they may be moderately underestimating hazard by not considering sources with 200 km of their region of interest. Their buffer zone for sources is presently 50 km.
}

\response{That is right. We increased the buffer zone up to 2 degrees.}

\comment{3}{%
It would be good if the abstract is more specific about the results. Where is the hazard greatest? What sources contribute to regions of higher hazard?
}
\response{Added to the abstract.}

@@

\comment{5}{%
line 39:   eight  $\to$ eighth
}
\response{Fixed.}

\comment{6}{%
line 55   focuses in $\to$ focuses on
}
\response{Done. Thanks.}

\comment{7}{%
line 56 $\to$ Please be more specific about how your analysis differs from previous analyses.
}
\response{Response will be here.}

\comment{8}{%
line 60 $\to$ Can you be more specific? What are the other indicators?
}
\response{We discussed this before. We need to remove the sentence and rewrite that part.}

@@

\comment{14}{%
line 180 $\to$ The smaller events should also help to inform the G-R relationship.
}
\response{Thanks for the comment. Added to the text.}

\comment{15}{%
line 182 $\to$ How come this study doesn't appear in Table 3. Do they not calculate PGA for 2 and 10\% exceedance in 50 years?
}
\response{They didn't provide a numerical value, or numbers on the contour lines, however, we read the images with Matlab and locate the values. We added to the table. Thanks.}

\comment{16}{%
line 192 $\to$ What is the total number of events before and after declustering?
}
\response{Number of events before decluttering: 10441, total foreshock: 971, total aftershock: 4206, declustered data 5254. It should be noted that, these numbers are representing the events in the study region (including the bufferzone). It partly includes events from Central and Zagros region. For completeness study we studied the whole data for each region.}

\comment{17}{%
line 224 $\to$ Why did you use this method? What are the benefits of one or the other?
}
\response{Both methods have been used extensively in previous studies. We just picked one. Text was implying that this method has beneficial to the ZMAP method, we fixed it. Thanks.}

@@

\comment{24}{%
line 335 $\to$ Different seismic zone will not necessarily have difference values of b and Mmax. Change to this: Different seismic zone may have different values of b and Mmax.
}
\response{Modified. Thanks.}

\comment{25}{%
line 337 $\to$ a means to reduce epistemic $\to$ a means to account for epistemic 
}
\response{Done.}

\comment{26}{%
line 361 $\to$ lead $\to$ leads
}
\response{Two reviewer suggested two different word. Both of them are correct. Please see.}

\comment{27}{%
line 364 $\to$ How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
}
\response{As mentioned in Atkinson and Adam (2013) and Atkinson et al (2014), using different GMPEs with different logic tree weights from different literature is not necessarily the best way to model the epistemic uncertainty in GMPEs. We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or central GMPE, and to define representative (upper and lower) GMPEs that express uncertainty about the central GMPE. In the previeous study (Khodaverdian 2016), they used Akkar and Bommer (2010) and Ghasemi et al (2009) along side other equations. Akkar and Bommer (2010) derived the equation up to 100 Km, which they used for 200 km. Also Ghasemi et al (2009) is presented the coefficients for spectral acceleration not PGA. Of course this alternative method has been a hotly-debated topic, and there is no clear consensus about that, however, the plots of attenuation relationships in different magnitude illustrate the fact that with this approach we can address the epistemic uncertainty in an acceptable range. We totally agree with the reviewer's comment that presenting the seismic hazard with upper and lower values (Fig 10) to address the epistemic uncertainty could be misleading for the readers. In order to address these concerns, we do the seismic hazard analysis for bigger domain (2 degrees buffer zone) and combine the results according to the logic tree scheme in Fig 9.}

@@

\comment{28}{%
line 365: add 'and'
}
\response{Added. Thanks.}

\comment{29}{%
line 370 $\to$ Could you consider other depths to help fill out your range of epistemic uncertainty?
}
\response{The Kalkan and Gulkan (2004) attenuation relationship is originally generated for Turkey. However, in the recent test by Zafarani and Mousavi (2014), it gives acceptable results for PGA. Since the high accuracy achieved by the current depth, and we have no idea how different depth will change the results, we prefer to not to use a parameter without knowing the effects. }

\comment{30}{%
line 371 $\to$ How does this value compare with the models you decided not to use?
}
\response{In revised version. We used backbone and plus and minus one standard deviation as three GMPEs. }

@@

\comment{31}{%
line 376 $\to$ In this case, you should consider all sources with 200 km of your area of interest.
}
\response{We modified the buffer zone. Thanks.}

\comment{32}{%
line 394:  50-years $\to$ 50-year
}
\response{Done.}

\comment{33}{%
line 420: with concentration $\to$ with a concentration
}
\response{Added. Thanks.}

\comment{34}{%
line 422 $\to$ I would have stated this differently. It looks like the lower b-value in Kopeh Dagh yields relatively high hazard in the R model whereas in the U model, this low b-value has leaked into the entire region and subsequently elevated seismic hazard in all areas outside of Kopeh Dagh.
}
\response{Based on the modification in GMPEs and uncertainties at the revised version, we rewrite the description part.}

\comment{35}{%
line 428 $\to$ Why equal weights?
}
\response{We added a comprehensive logic tree analysis after revision and modified the weights. Please see figure 9.}

@@

\comment{41}{%
line 455 $\to$ 0.27-0.31 g for 10\% probability of exceedance $\to$  0.27-0.31 g for the same exceedance probability
}
\response{Done.}

\comment{42}{%
line 458 $\to$  for 2 and 10\% ? for 2 and 10\% in 50 years
}
\response{Done.}

\comment{43}{%
line 461: our results are close or within $\to$ our results are close to or within 
}
\response{Done.}

\comment{44}{%
line 462 $\to$ Can you explain the differences in their analysis relative to yours that lead to higher values?
}
\response{They used Maximum Credible Earthquake as $M_{max}$. The maximum credible earthquake is largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, as based on geologic and seismologic data, so it is higher than observation or data driven $M_{max}$. }

\comment{45}{%
line 466: exceedance as functions of PGA  $\to$ exceedance as functions of PGA, also known as hazard curves}
\response{Added. Thanks.}

@@

\comment{46}{%
line 475 $\to$ Can you explain the differences in the hazard analysis that led to differences in hazard?}
\response{Response will be here.}

\comment{47}{%
lline 488 $\to$ Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g. you only use one GMPE (though you do consider two b-value and Mmax based models).
}
\response{Response will be here.}

\comment{48}{%
line 488:  hazard analysis $\to$ hazard analyses
}
\response{Done.}

\comment{49}{%
line 490: models as a mean $\to$ models as a means}
\response{Done.}

\comment{50}{%
line 493 $\to$ Though you suggest the uniform model is unrealistic on line 334.}
\response{That's right. We meant to say less realistic. We fixed the text.}

\comment{51}{%
line 502 $\to$ for providing advise ? for providing advice}
\response{Done.}

\comment{52}{%
line 509 $\to$  Should this be Sunset?}
\response{Yes. Thanks.}

\comment{53}{%
p 25, table2 $\to$ What did you do for the earthquakes occurring outside of these five zones?}
\response{There are earthquakes out of the regions, mainly above the Caspian see. Since those area are not in our region of interest (They mainly are in country of Azerbaijan), and are fairly far from our region, we ignored them.}

\comment{54}{%
p 26, table3 $\to$ Specify units.}
\response{Done. Thanks.}

\comment{55}{%
p32, figure 3 $\to$ You should also show events in the buffer zone used to compute hazard.}
\response{Done.}

\comment{56}{%
p34, figure 5 $\to$ Which seismic zone corresponds to which color? It looks like either reporting or rates have changed over time. For example, I might argue that the red region was not complete for M3 and above until 2005. }
\response{Thanks for the comment. The problem with that region is having less than and equal sign on magnitude 4. There are many earthquakes go to that category because of that condition. Since, converting earthquake magnitude always has an error margin, we think the comment is relevant. Based on the data we assume 2005 as a completeness magnitude. We presented the legends at the bottom of the figure.}

\comment{57}{%
P37: 10 percent of probability $\to$ 10 percent probability }
\response{Done.}

\comment{58}{%
p 39,figure 11: Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.}
\response{Included.}

\comment{59}{%
p 41, figure 12: Can you include curves or points for the other studies in Table 3?}
\response{Added.}

### 2016-10-18 completeness.tex
Addressed remaining comments, except three of them.

Determining the completeness magnitude $M_c$, on the other hand, is often determined using simple numerical analysis in combination with data inspection. Two common approaches are maximum curvature and the goodness-of-fit test methods. The maximum curvature method, or MAXC for simplicity, is widely used because as it has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}. \citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East. We use the goodness-of-fit test method introduced by \citet{Wiemer2000}, and compute $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.

>>>>

Determining the completeness magnitude $M_c$, on the other hand, is often determined using simple numerical analysis in combination with data inspection. Two common approaches are maximum curvature and the goodness-of-fit test methods. \myrevision{Both methods have been used extensively at previous studies}.The maximum curvature method, or MAXC for simplicity, is widely used because as it has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}. \citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East. \myrevison{\citet{Moscheti2015} applied a combination of methods to study the  long-term earthquake rate model for the Central and Eastern United States.} We use the goodness-of-fit test method introduced by \citet{Wiemer2000}, and compute $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.

### 2016-10-18 introduction.tex
Addressed remaining comments, except three of them.

\myrevision{Most previous studies focus on particular locations  based on specific categorization of seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.} We use the smoothed seismicity method introduced by \citet{Frankel1995}. This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}. Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting. While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored. In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}). In addition to this five seismic-zone model, we obtain results for the entire region of interest as if it could be considered as a single uniform seismic zone. We used both these models and the combination of them to interpret seismic hazard in northern Iran.

>>>>

\myrevision{Most previous studies focus on particular locations  based on specific categorization of seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.} We use the smoothed seismicity method introduced by \citet{Frankel1995}. This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}. \myrevision{In \citep{Khodaverdian_2016_BSSA}, seismicity parameters like $b-value$ and $M_{max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree. Earthquake catalog for each grid point is all events within 200 km buffer zone surrounding the grid point. Whereas in this study, we assume the seismic parameters are uniform for each tectonic seismic region.} Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting. While we recognize that \myrevision{fault-based/geologic-based earthquake recurrence estimates } can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored. In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}). In addition to this five seismic-zone model, we obtain results for the entire region of interest as if it could be considered as a single uniform seismic zone. We used both these models and the combination of them to interpret seismic hazard in northern Iran.

### 2016-10-18 parameters.tex
Rewrote part of the results.and attributes.
Addressed remaining comments, except three of them.

The $a$-value is estimated based on the completeness year, the correlation distance, and the number of events per grid cell. We assume magnitude increments of $\Delta M = 0.1$, count events with magnitude $M_w > 3$, and smooth the number of events for each cell. This means each cell has a different $a$-value and thus the result is variable throughout our region of interest. On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area. We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog. \myrevision{ Regional maximum magnitude is estimated according to \citet{Kijko1989} method. Magnitude errors are distributed normally and $\beta$ and $\lambda$ are calculated simultaneously.  We divide the} catalog in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015. In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.

We obtain $b$ and $M_{\max}$ for two different models. In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran. We call this the \textit{R Model}. In it we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference). In the second model we consider the whole study area as a uniform seismic zone. We call it the \textit{U Model}. Admittedly, this assumption is somewhat unrealistic if considered from the point of view that different seismic zones \myrevision{may have different values of $b$ and $M_{max}$}. However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to \myrevision{account for} epistemic uncertainty. Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
\myrevision{
\begin{table}%[t]
    \centering
    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
        \cline{2-4}                                                                         \\[-1.6ex]
                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
        \hline                                                                              \\[-1.6ex]
        Azerbaijan      & 1.15 $\pm$ 0.03   & 7.80 $\pm$ 0.50   & 7.7                       \\
        Alborz          & 0.97 $\pm$ 0.02   & 7.82 $\pm$ 0.52   & 7.8                       \\
        Kopeh Dagh      & 0.93 $\pm$ 0.03   & 7.74 $\pm$ 0.29   & 7.6                       \\
        Zagros          & 1.05 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
        Central-East    & 0.99 $\pm$ 0.02   & 7.80 $\pm$ 0.37   & 7.6                       \\
        Uniform Model   & 0.98 $\pm$ 0.01   & 7.80 $\pm$ 0.28   & 7.8                       \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:params} 
\end{table}
}
\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-07} 
    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest. The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country. The last curve in green corresponds to the complete region of interest, here referred to as the uniform model. The shaded range indicates the models' $\pm 1$ standard deviation.}
    \label{fig:annualp}
\end{figure*}

>>>>

The $a$-value is estimated based on the completeness year, the correlation distance, and the number of events per grid cell. We assume magnitude increments of $\Delta M = 0.1$, count events with magnitude $M_w > 3$, and smooth the number of events for each cell. This means each cell has a different $a$-value and thus the result is variable throughout our region of interest. On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area. We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog. \myrevision{ Regional maximum magnitude is estimated according to \citet{Kijko_1989_BSSA} method. Magnitude errors are distributed normally and $\beta$ and $\lambda$ are calculated simultaneously.  We divide the} catalog in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015. In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.

We obtain $b$ and $M_{\max}$ for two different models. In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran. We call this the \textit{R Model}. In it we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference). In the second model we consider the whole study area as a uniform seismic zone. We call it the \textit{U Model}. Admittedly, this assumption is somewhat \myrevision{less-realistfic} if considered from the point of view that different seismic zones \myrevision{may have different values of $b$ and $M_{max}$}. However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to \myrevision{account for} epistemic uncertainty. Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
\myrevision{
\begin{table}%[t]
    \centering
    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
        \cline{2-4}                                                                         \\[-1.6ex]
                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
        \hline                                                                              \\[-1.6ex]
        Azerbaijan      & 1.15 $\pm$ 0.03   & 7.80 $\pm$ 0.50   & 7.7                       \\
        Alborz          & 0.97 $\pm$ 0.02   & 7.82 $\pm$ 0.52   & 7.8                       \\
        Kopeh Dagh      & 0.93 $\pm$ 0.03   & 7.74 $\pm$ 0.29   & 7.6                       \\
        Zagros          & 1.05 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
        Central-East    & 0.99 $\pm$ 0.02   & 7.80 $\pm$ 0.37   & 7.6                       \\
        Uniform Model   & 0.98 $\pm$ 0.01   & 7.80 $\pm$ 0.28   & 7.8                       \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:params} 
\end{table}
}
\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-07} 
    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest. The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country. The last curve in green corresponds to the complete region of interest, here referred to as the uniform model. The shaded range indicates the models' $\pm 1$ standard deviation.}
    \label{fig:annualp}
\end{figure*}

### 2016-10-18 results.tex
updated to match figure files
Addressed remaining comments, except three of them.

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-08.pdf}
    \caption{Expected mean peak ground acceleration (PGA) for 2 and 10 percent of probability of exceedance in 50 years for (a) the five-seismic regions R model and (b) the uniform seismic region U model.}
    \label{fig:pga}
\end{figure*}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-09.pdf}
    \caption{Difference between the mean PGA values from models U and R for 2 (left) and 10 (right) percent probabilities of exceedance in 50 years.}
    \label{fig:pga.diff}
\end{figure*}

@@

As it can be seen in Fig.~\ref{fig:pga.ru.std}, the combined (R,U) model follows more closely the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as the major faults shown in Fig.~\ref{fig:selected}a, and thus we consider it to be a better assessment of the seismic hazard in the region. It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the North Alborz fault in the Alborz region and that of the different faults in the Kopeh Dagh region. In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2 model results, where the expected accelerations are of the order of 1.0 g to the northwest of \myrevision{the} city of Tabriz. These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects or other related conditions which may often contribute to mitigating peak accelerations.

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-10.pdf}
    \caption{Expected mean peak ground acceleration (PGA) for 2 and 10 percent of probability of exceedance in 50 years for (a) the five-seismic regions R model and (b) the uniform seismic region U model.}
    \label{fig:pga}
\end{figure*}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-11.pdf}
    \caption{Difference between the mean PGA values from models U and R for 2 (left) and 10 (right) percent probabilities of exceedance in 50 years.}
    \label{fig:pga.diff}
\end{figure*}

@@

As it can be seen in Fig.~\ref{fig:pga.ru.std}, the combined (R,U) model follows more closely the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as the major faults shown in Fig.~\ref{fig:selected}a. It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the North Alborz fault in the Alborz region and that of the different faults in the Kopeh Dagh region. In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2 model results, where the expected accelerations are of the order of 1.0 g to the northwest of \myrevision{the} city of Tabriz. These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects or other related conditions which may often contribute to mitigating peak accelerations.
